Fourmile Calibrations

### 2023-01-24 calibration_output.Rmd
added cumulative flows, percentiles, catchment precip & tmean

q <- ggplot(flow_pivot, aes(date, q_m3s, color = cal_run)) +
  geom_line()

@@

plotq_cy <- function(calyear) {
  {flow_pivot %>%
    filter(year == calyear) %>%
    ggplot(aes(x = date,
               y = q_m3s,
               color = cal_run)) +
    geom_line() +
    ggtitle(calyear) +
    theme_bw()} %>%
    ggplotly()

@@

@@

kge_plot_cy <- ggplot(flow_plot, aes(year, kge, color = model_run)) + geom_point(size = 3) +
  theme_bw()

@@

q_ensemble <- ggplot(ensem_pivot, aes(date, q_m3s, color = cal_run)) +
  geom_line()

@@

plotqensem_cy <- function(calyear) {
  {ensem_pivot %>%
    filter(year == calyear) %>%
    ggplot(aes(x = date,
               y = q_m3s,
               color = cal_run)) +
    geom_line() +
    ggtitle(calyear) +
    theme_bw()} %>%
    ggplotly()

@@

@@

kge_plot_mo <- ggplot(mo_pivot, aes(month, KGE, color = cal_run)) + geom_point(size = 3) +
  theme_bw()

@@

rmse_plot_mo <- ggplot(mo_pivot2, aes(month, RMSE, color = cal_run)) + geom_point(size = 3) +
  theme_bw()

@@

mo_nse <- ensem %>%
  ungroup() %>%
  mutate(month = month(date)) %>%
  group_by(month) %>%
  summarize(grid_ensemble = NSE(grid_ensemble, obs),
            statn_ensemble = NSE(statn_ensemble, obs),
            all_ensemble = NSE(all_ensemble, obs),
            grid_all = NSE(grid_all, obs),
            statn_all = NSE(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 4)

@@

nse_plot_mo <- ggplot(mo_pivot2, aes(month, nse, color = cal_run)) + geom_point(size = 3) +
  theme_bw()

@@

@@

@@

mo_pbias <- ensem %>%
  ungroup() %>%
  mutate(month = month(date)) %>%
  group_by(month) %>%
  summarize(grid_ensemble = pbias(grid_ensemble, obs),
            statn_ensemble = pbias(statn_ensemble, obs),
            all_ensemble = pbias(all_ensemble, obs),
            grid_all = pbias(grid_all, obs),
            statn_all = pbias(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 4)

@@

pbias_plot_mo <- ggplot(mo_pivot2, aes(month, pbias, color = cal_run)) + geom_point(size = 3) +
  theme_bw()

@@

```{r}

ensem_cumq <- ensem %>%
  mutate(month = month(date)) %>%
  filter(month %in% c(4:9)) %>%
  select(-month) %>% 
  pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
  group_by(cal_run, year(date)) %>%
  mutate(cumsum = cumsum(replace_na(q_m3s, 0))) %>%
  rename(year = 4) %>%
  mutate(year = as.factor(year))

#plot annual cumulative Q vals for ensembles
plot_cumulq_yr_ensem <- function(calyear) {
  {ensem_cumq %>%
    filter(year == calyear) %>%
    ggplot(aes(x = date,
               y = cumsum,
               color = cal_run)) +
    geom_line() +
    geom_line(data=ensem_cumq[ensem_cumq$cal_run=='obs',], aes(group=cal_run), color = "black") +
    ggtitle(calyear) +
    theme_bw() +
    labs(y = 'cumulative Q (m3s)')} %>%
    ggplotly()
}

@@

>>>>

q <- ggplot(flow_pivot, aes(date, q_m3s, color = cal_run)) +
  geom_line() +
  scale_color_manual(name="cal_run", values=c('obs' = 'black',
                                            "grid_2011"="seagreen", 
                                            "grid_2012"="seagreen2", 
                                            "grid_2013"="steelblue",
                                            "grid_2014"='dodgerblue', 
                                            "grid_2015" = "cyan3",
                                            'grid_2016' = 'blue',
                                            'grid_2017' = 'blue4',
                                            'grid_2018' = 'cadetblue',
                                            'grid_2019' = 'lightgreen',
                                            'grid_2020' = 'olivedrab',
                                            'grid_all' = 'steelblue3',
                                            "statn_2011"="maroon", 
                                            "statn_2012"="deeppink4", 
                                            "statn_2013"="deeppink",
                                            "statn_2014"='purple', 
                                            "statn_2015" = "mediumorchid1",
                                            'statn_2016' = 'indianred',
                                            'statn_2017' = 'sienna',
                                            'statn_2018' = 'salmon2',
                                            'statn_2019' = 'mediumpurple1',
                                            'statn_2020' = 'violetred',
                                            'statn_all' = 'red'))

@@

plotq_cy <- function(calyear) {
  {flow_pivot %>%
    filter(year == calyear) %>%
    ggplot(aes(x = date,
               y = q_m3s,
               color = cal_run)) +
    geom_line() +
        scale_color_manual(name="cal_run", values=c('obs' = 'black',
                                            "grid_2011"="seagreen", 
                                            "grid_2012"="seagreen2", 
                                            "grid_2013"="steelblue",
                                            "grid_2014"='dodgerblue', 
                                            "grid_2015" = "cyan3",
                                            'grid_2016' = 'blue',
                                            'grid_2017' = 'blue4',
                                            'grid_2018' = 'cadetblue',
                                            'grid_2019' = 'lightgreen',
                                            'grid_2020' = 'olivedrab',
                                            'grid_all' = 'steelblue3',
                                            "statn_2011"="maroon", 
                                            "statn_2012"="deeppink4", 
                                            "statn_2013"="deeppink",
                                            "statn_2014"='purple', 
                                            "statn_2015" = "mediumorchid1",
                                            'statn_2016' = 'indianred',
                                            'statn_2017' = 'sienna',
                                            'statn_2018' = 'salmon2',
                                            'statn_2019' = 'mediumpurple1',
                                            'statn_2020' = 'violetred',
                                            'statn_all' = 'red')) +
    ggtitle(calyear) +
    theme_bw()} %>%
    ggplotly()

@@

try
```

@@

kge_plot_cy <- ggplot(flow_plot, aes(year, kge, color = model_run)) + 
  geom_point(size = 3) +
  scale_color_manual(name="model_run", values=c("grid2011"="seagreen", 
                                            "grid2012"="seagreen2", 
                                            "grid2013"="steelblue",
                                            "grid2014"='dodgerblue', 
                                            "grid2015" = "cyan3",
                                            'grid2016' = 'blue',
                                            'grid2017' = 'blue4',
                                            'grid2018' = 'cadetblue',
                                            'grid2019' = 'lightgreen',
                                            'grid2020' = 'olivedrab',
                                            'gridall' = 'steelblue3',
                                            "statn2011"="maroon", 
                                            "statn2012"="deeppink4", 
                                            "statn2013"="deeppink",
                                            "statn2014"='purple', 
                                            "statn2015" = "mediumorchid1",
                                            'statn2016' = 'indianred',
                                            'statn2017' = 'sienna',
                                            'statn2018' = 'salmon2',
                                            'statn2019' = 'mediumpurple1',
                                            'statn2020' = 'violetred',
                                            'statnall' = 'red')) +
  theme_bw()

@@

q_ensemble <- ggplot(ensem_pivot, aes(date, q_m3s, color = cal_run)) +
  geom_line() +
  scale_color_manual(name="cal_run", values=c('obs'='black',
                                            "grid_ensemble"="maroon", 
                                            "statn_ensemble"="darkturquoise", 
                                            "grid_all"="purple1",
                                            "statn_all"='springgreen4', 
                                            "all_ensemble" = "orange"))

@@

plotqensem_cy <- function(calyear) {
  {ensem_pivot %>%
    filter(year == calyear) %>%
    ggplot(aes(x = date,
               y = q_m3s,
               color = cal_run)) +
    geom_line() +
    scale_color_manual(name="cal_run", values=c('obs' = 'black',
                                            "grid_ensemble"="maroon", 
                                            "statn_ensemble"="darkturquoise", 
                                            "grid_all"="purple1",
                                            "statn_all"='springgreen4', 
                                            "all_ensemble" = "orange")) +
    ggtitle(calyear) +
    theme_bw()} %>%
    ggplotly()

@@

try

@@

kge_plot_mo <- ggplot(mo_pivot, aes(month, KGE, color = cal_run)) + geom_point(size = 3) +
    scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon", 
                                            "statn_ensemble"="darkturquoise", 
                                            "grid_all"="purple1",
                                            "statn_all"='springgreen4', 
                                            "all_ensemble" = "orange")) +
  theme_bw()

@@

rmse_plot_mo <- ggplot(mo_pivot2, aes(month, RMSE, color = cal_run)) + geom_point(size = 3) +
    scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon", 
                                            "statn_ensemble"="darkturquoise", 
                                            "grid_all"="purple1",
                                            "statn_all"='springgreen4', 
                                            "all_ensemble" = "orange")) +
  theme_bw()

@@

mo_nse <- ensem %>%
  ungroup() %>%
  drop_na() %>% 
  mutate(month = month(date)) %>%
  group_by(month) %>%
  summarize(grid_ensemble = NSE(grid_ensemble, obs),
            statn_ensemble = NSE(statn_ensemble, obs),
            all_ensemble = NSE(all_ensemble, obs),
            grid_all = NSE(grid_all, obs),
            statn_all = NSE(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 4)

@@

nse_plot_mo <- ggplot(mo_pivot2, aes(month, nse, color = cal_run)) + geom_point(size = 3) +
  theme_bw() +
  scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon", 
                                            "statn_ensemble"="darkturquoise", 
                                            "grid_all"="purple1",
                                            "statn_all"='springgreen4', 
                                            "all_ensemble" = "orange"))

@@

```{r pbias all, echo = F}

@@

```{r annualpbias, echo = F}

@@

```{r monthly pbias, echo =F}

mo_pbias <- ensem %>%
  ungroup() %>%
  drop_na() %>% 
  mutate(month = month(date)) %>%
  group_by(month) %>%
  summarize(grid_ensemble = pbias(grid_ensemble, obs),
            statn_ensemble = pbias(statn_ensemble, obs),
            all_ensemble = pbias(all_ensemble, obs),
            grid_all = pbias(grid_all, obs),
            statn_all = pbias(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 4)

@@

pbias_plot_mo <- ggplot(mo_pivot2, aes(month, pbias, color = cal_run)) + 
  geom_point(size = 3) +
  scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon", 
                                            "statn_ensemble"="darkturquoise", 
                                            "grid_all"="purple1",
                                            "statn_all"='springgreen4', 
                                            "all_ensemble" = "orange")) +
  theme_bw()

@@

```{r cumq, echo = F}

ensem_cumq <- ensem %>%
  mutate(month = month(date)) %>%
  filter(month %in% c(4:9)) %>%
  select(-month) %>% 
  pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
  group_by(cal_run, year(date)) %>%
  mutate(cumsum = cumsum(replace_na(q_m3s, 0))) %>%
  rename(year = 4) %>%
  mutate(year = as.factor(year)) %>%
  ungroup()

#plot annual cumulative Q vals for ensembles
plot_cumulq_yr_ensem <- function(calyear) {
  {ensem_cumq %>%
    filter(year == calyear) %>%
    ggplot(aes(x = date,
               y = cumsum,
               color = cal_run)) +
    geom_line() +
    scale_color_manual(name="cal_run", values=c("obs"="black",
                                             "grid_ensemble"="maroon", 
                                            "statn_ensemble"="darkturquoise", 
                                            "grid_all"="purple1",
                                            "statn_all"='springgreen4', 
                                            "all_ensemble" = "orange")) +
    ggtitle(calyear) +
    theme_bw() +
    labs(y = 'cumulative Q (m3s)')} %>%
    ggplotly()
}

@@

## Percentiles

```{r percentiles, echo = F}

quantile_calc <- function(x, probs, date) {
  tibble(x = quantile(x, probs), probs = probs,
         date = date[x = quantile(x, probs)])
}

percent <- ensem_cumq %>%
  group_by(year, cal_run) %>%
  summarize(quantile_calc(cumsum, c(0.25, 0.5, 0.75), date)) %>%
  mutate(date = as.Date(date)) %>%
  mutate(probs = as.factor(probs))

###
# quantile_cal <- function(data, prob) {
#   data %>%
#     dplyr::group_by(cal_run, year) %>%
#     mutate(quantile = paste0(prob),
#            value = quantile(cumsum, prob)) %>%
#     filter(cumsum >= value) %>%
#     filter(date == min(date))
#   }
# 
# quantiles <- c(0.25, 0.5, 0.75)
# 
# quants <- quantiles %>% 
#   map(~ quantile_cal(data = ensem_cumq, prob = .)) %>%
#   bind_rows()
####

#plot percentiles
plot_perc_ensem <- function(perc) {
  {percent %>%
    filter(probs == perc) %>%
    ggplot(aes(x = year,
               y = x,
               color = cal_run)) +
    geom_point(size=3) +
    scale_color_manual(name="cal_run", values=c("obs"="black",
                                             "grid_ensemble"="maroon", 
                                            "statn_ensemble"="darkturquoise", 
                                            "grid_all"="purple1",
                                            "statn_all"='springgreen4', 
                                            "all_ensemble" = "orange")) +
    ggtitle(perc) +
    ylab('Streamflow (cms)') +
    theme_bw()} %>%
    ggplotly()
}

name <- levels(percent$probs)

perc_plots <- lapply(name, perc_plots)

htmltools::tagList(plot_perc_ensem)

perc_plots

# Catchment results

```{r catch, echo = F}

setwd("C:/Users/sears/Documents/Repos/fourmile/catchments")

statn <- read_csv('statnall.csv')
grid <- read_csv('gridall.csv')

grid <- grid %>% mutate(site = 'grid')
statn <- statn %>% mutate(site = 'statn')

catchment <- bind_rows(grid, statn) %>%
  mutate(year = as.factor(year(time))) %>%
  group_by(year, site) %>%
  mutate(cumulative_p = cumsum(precip))

#plot cumulative precip by year
plot_cumprecip <- function(calyear) {
  {catchment %>%
    filter(year == calyear) %>%
    ggplot(aes(x = time,
               y = cumulative_p, color = site)) +
    geom_line(size=1) +
    ggtitle(calyear) +
    ylab('Cumulative precip (mm)') +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust=1))} %>%
    ggplotly()
}

name <- levels(catchment$year)

precip_plots <- lapply(name, plot_cumprecip)

htmltools::tagList(precip_plots)

precip_plots

## total P
max_cumulativep <- catchment %>%
  group_by(year, site) %>%
  summarize(total_cumulativep = max(cumulative_p))

ggplot(max_cumulativep, aes(x=year, y=total_cumulativep, color=site)) + 
  geom_point(size=3) +
  ggtitle('Total cumulative precip (mm) by year')

##tmean 
tmean <- catchment %>%
  group_by(year, site) %>%
  summarize(tmean = mean(tmean)) %>%
  ggplot(aes(x = year, y=tmean, color = site)) +
  geom_point(size=3) +
  ggtitle('Average temp by year')

tmean
